Who we are affects how we vote

### 2019-05-06 elections_conversation.Rmd
Working on graphs

>>>>

```{r income, fig.cap = "Estimated age effect for each election, which represents the impact of electorate median age on the two-party preferred vote. Higher values indicate a ", fig.pos="H"}
coefs %>% filter(variable=="Income") %>%
  ggplot(aes(x=year)) +
  geom_hline(aes(yintercept = 0), col='gray', size = 1) +
  geom_point(aes(x = year, y = estimate), size = 2) +
  geom_linerange(aes(x = year, ymin = lower95, ymax = upper95), size = 1.2) +
  labs(x = "Election year", y = "2PP impact") +
  coord_fixed(ratio = 0.25) + 
  scale_x_continuous(breaks=seq(2001,2016,by=3), minor_breaks=NULL)
```
